---
title: Experimental Validation of Architectural Measures for Cloud-native Quality Evaluations - Results
date: "2025-02-24"
author: Robin Lichtenthäler
header-includes:
  - \usepackage{subfig}
  - \usepackage{caption}
urlcolor: blue
linkcolor: RoyalBlue
output: 
  bookdown::html_document2:
  bookdown::pdf_document2:  
    latex_engine: xelatex    # bookdown needs to be installed: install.packages("bookdown")
    keep_tex: true
always_allow_html: true
mainfont: DejaVu Sans # if not available, install it from https://dejavu-fonts.github.io/
sansfont: DejaVu Sans
monofont: DejaVu Sans Mono
---


```{r load-packages, include=FALSE}
library(extrafont)
#library(tidyverse)
library(hrbrthemes)
library(viridis)
library(plyr)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(anytime)
library(knitr)
library(ggplot2)
library(hash)
library(gridExtra)
library(showtext)
#library(ggpubr)
#library(ggtext)
library(kableExtra)
library(XNomial)
showtext_auto()
library(modelsummary)


```

\newpage

# Introduction{#intro}

In the context of the paper "An experimental validation of architectural measures for cloud-native quality evaluations" experiments have been run to investigate relationship between architectural measures (measured at design time) and runtime measures (measured at runtime).
The results of these experiments are reported in the following and can be accessed in raw form at: <Repo URl>


```{r, include=FALSE, cache=FALSE}
extrafont::loadfonts(device="all", quiet = TRUE)


resultsPath = "./results"
resultFolders = c("/original/teastore-private-nlb-original"
                  ,"/serviceReplication/teastore-private-nlb-highreplication"
                  ,"/serviceReplication/teastore-private-nlb-lowreplication"
                  ,"/serviceReplication/teastore-private-nlb-mixedreplication"
                  ,"/serviceReplication/teastore-private-nlb-withfailures-noreplication"
                  ,"/serviceReplication/teastore-private-nlb-withfailures-lowreplication"
                  ,"/serviceReplication/teastore-private-nlb-withfailures-mixedreplication"
                  ,"/serviceReplication/teastore-private-nlb-withfailures-highreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-single-noreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-single-highreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-two-noreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-two-highreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-three-noreplication"
                  ,"/horizontalDataReplication/teastore-private-nlb-rds-three-highreplication"
                  ,"/verticalReplication/teastore-private-nlb-noreplication-nocaching"
                  ,"/verticalReplication/teastore-private-nlb-noreplication-withcaching"
                  ,"/verticalReplication/teastore-private-nlb-noreplication-withmorecaching"
                  ,"/verticalReplication/teastore-private-nlb-withfailures-nocaching"
                  ,"/verticalReplication/teastore-private-nlb-withfailures-withcaching"
                  ,"/verticalReplication/teastore-private-nlb-withfailures-withmorecaching"
);


loadData <- function(path, subPath) {
  return(read.csv2(paste(path,subPath,".csv", sep=""), sep=",", check.names = FALSE))
}

getRequestTraceNameFromMeasures <- function(nameFromExperiment) {
  return(
   switch(nameFromExperiment, 
           "Add Product 2 to Cart"="Add Product To Cart",
           "Add Product to Cart"="Add Product To Cart",
           "Home"="Index Page",
           "List Products"="Show Category",
           "List Products with different page"="Show Category",
           "Login"="User Login",
           "Logout"="User Logout",             
           "Look at Product"="Product Page",
           #"Add Product 2 to Cart - discrete"="Add Product To Cart",
           #"Add Product to Cart - discrete"="Add Product To Cart",
           #"Home - discrete"="Index Page",
           #"List Products - discrete"="Show Category",
           #"List Products with different page - discrete"="Show Category",
           #"Login - discrete"="User Login",
           #"Logout - discrete"="User Logout",             
           #"Look at Product - discrete"="Product Page",
           "n/a"
    )
  )
}


coalesce_join <- function(x, y, 
                          by = NULL, suffix = c(".x", ".y"), 
                          join = dplyr::full_join, ...) {
  joined <- join(x, y, by = by, suffix = suffix, ...)
  # names of desired output
  cols <- union(names(x), names(y))
  
  to_coalesce <- names(joined)[!names(joined) %in% cols]
  suffix_used <- suffix[ifelse(endsWith(to_coalesce, suffix[1]), 1, 2)]
  # remove suffixes and deduplicate
  to_coalesce <- unique(substr(
    to_coalesce, 
    1, 
    nchar(to_coalesce) - nchar(suffix_used)
  ))
  
  coalesced <- purrr::map_dfc(to_coalesce, ~dplyr::coalesce(
    joined[[paste0(.x, suffix[1])]], 
    joined[[paste0(.x, suffix[2])]]
  ))
  names(coalesced) <- to_coalesce
  
  dplyr::bind_cols(joined, coalesced)[cols]
}


addMeasures <- function(resultSet, resultsPath, subPath) {
  measures <- read.csv2(paste(resultsPath, subPath, "-model-measures.csv", sep=""))
  systemMeasures <- measures %>% 
    filter(entityType == "system") %>% 
    filter(measureKey %in% c("serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel", "ratioOfCachedDataAggregates", "")) %>% 
    select (-c(measureName, systemName, entityId)) %>% 
    pivot_wider(
      names_from = measureKey, 
      values_from = value
    )
  
  requestTraceMeasures <- measures %>% 
    filter(entityType == "requestTrace") %>% 
    filter(measureKey %in% c("dataReplicationAlongRequestTrace", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel")) %>% 
    select (-c(measureName, systemName, entityId)) %>% 
    pivot_wider(
      names_from = measureKey, 
      values_from = value
    )
  
  resultSet <- resultSet %>% left_join(systemMeasures, by=join_by(entityType == entityType))
  resultSet <- resultSet %>% mutate(requestTraceName = unlist(lapply(label, getRequestTraceNameFromMeasures))) %>% coalesce_join(requestTraceMeasures, by=join_by(requestTraceName == entityName), join=dplyr::left_join)
  resultSet <- resultSet %>% mutate("entityName" = coalesce(entityName, requestTraceName)) %>% relocate("entityName", .after="entityType") %>% select (-c("requestTraceName"))
  
  resultSet <- resultSet %>% mutate_at(c("dataReplicationAlongRequestTrace", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel"), as.character) %>%
    mutate_at(c("dataReplicationAlongRequestTrace", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel"), as.numeric)
  return(resultSet)
}

combinedLoad <- function(path) {
  rawResultSet <- loadData(resultsPath, path)
  rawResultSet <- rawResultSet %>% select (-c("mean(latency) [ms]", "median(latency) [ms]", "90th_percentile(latency) [ms]", "mean(receivedBytes) [byte]", "median(receivedBytes) [byte]", "90th_percentile(receivedBytes) [byte]", "mean(sentBytes) [byte]")) %>%
    filter(!str_detect(label, "- discrete")) %>%
    relocate("entityType", .before="mean(elapsed) [ms]") %>%
    relocate("label", .before="entityType") %>%
    relocate("architectureVariation", .before="label" )
  
  rawResultSet["success_rate [%]"] <- as.numeric(unlist(rawResultSet["success_rate [%]"])) * 100
  
  # TODO find a better, more generic solution
  rawResultSet["mean(elapsed) [ms]"] <- as.numeric(unlist(rawResultSet["mean(elapsed) [ms]"]))
  rawResultSet["90th_percentile(elapsed) [ms]"] <- as.numeric(unlist(rawResultSet["90th_percentile(elapsed) [ms]"]))
  rawResultSet["throughput [requests / s]"] <- as.numeric(unlist(rawResultSet["throughput [requests / s]"]))
  
  combinedResultSet <- addMeasures( rawResultSet, resultsPath, path )
  
  combinedResultSet <- combinedResultSet %>%
    mutate(architectureVariation=str_remove(architectureVariation, "teastore-private-nlb-")) %>% 
    mutate(entityName = ifelse(entityType == "system", "teaStore", entityName))
  
  combinedResultSet["serviceReplicationLevel"] <- as.numeric(unlist(combinedResultSet["serviceReplicationLevel"]))
  combinedResultSet["medianServiceReplication"] <- as.numeric(unlist(combinedResultSet["medianServiceReplication"]))
  combinedResultSet["smallestReplicationValue"] <- as.numeric(unlist(combinedResultSet["smallestReplicationValue"]))
  combinedResultSet["storageReplicationLevel"] <- as.numeric(unlist(combinedResultSet["storageReplicationLevel"]))
  combinedResultSet["ratioOfCachedDataAggregates"] <- as.numeric(unlist(combinedResultSet["ratioOfCachedDataAggregates"]))
  combinedResultSet["dataReplicationAlongRequestTrace"] <- as.numeric(unlist(combinedResultSet["dataReplicationAlongRequestTrace"]))
  
  combinedResultSet <- combinedResultSet %>% mutate_if(is.numeric, ~round(., 2))
  
  return(combinedResultSet)
}


for (result in resultFolders) {
  fullPath <- paste(resultsPath, result, sep="");

  variationName <- tail(str_split_1(result, "/"), n=1);
  transformedName <- gsub("-(.)", "\\U\\1", variationName, perl = TRUE)  # Capitalize letters following hyphens
  transformedName <- gsub("-", "", transformedName)  # Remove hyphens
  
  assign(transformedName, combinedLoad(result)) # load data
}


teastorePrivateNlbNoreplication <- teastorePrivateNlbOriginal %>% mutate("architectureVariation" = "noreplication")

# actual analysis

theme_set(theme_bw())  # pre-set the bw theme.
plotResult <- function(data, entityName, xVar, yVar, legendPos) {
  if (legendPos == "tr") {
    legendPosValues <- c(0.8,0.8)
  } else if (legendPos == "br") {
    legendPosValues <- c(0.8,0.2)
  } else if (legendPos == "bl") {
    legendPosValues <- c(0.2,0.2)
  } else if (legendPos == "tl") {
    legendPosValues <- c(0.2,0.8)
  } else {
    legendPosValues <- "left"
  }
  
  ggplot(data %>% filter(entityName == {{entityName}}), aes(x={{xVar}}, y={{yVar}}, colour = architectureVariation, shape = factor(loadLevel))) + 
    geom_point(size=2) +
    labs(color = "Architecture variation", shape ="Load level [req/s]") +
    theme(legend.position = legendPosValues,
          legend.spacing.y = unit(0, "mm"), 
          axis.text = element_text(colour = 1, size = 10),
          legend.background = element_blank(),
          legend.box.background = element_rect(colour = "black"))
}

plotResultWithRegression <- function(data, entityName, xVar, yVar, form, legendPos) {
  if (legendPos == "tr") {
    legendPosValues <- c(0.8,0.8)
  } else if (legendPos == "br") {
    legendPosValues <- c(0.8,0.2)
  } else if (legendPos == "bl") {
    legendPosValues <- c(0.2,0.2)
  } else if (legendPos == "tl") {
    legendPosValues <- c(0.2,0.8)
  } else {
    legendPosValues <- "left"
  }
  
  linearModel = lm(formula(form), data = data %>% filter(entityName == {{entityName}})) # linear regression
  summary(linearModel) #Review the results

  ggplot(data %>% filter(entityName == {{entityName}}), aes(x={{xVar}}, y={{yVar}}, colour = architectureVariation, shape = factor(loadLevel))) + 
    geom_point(size=2) +
    labs(title= paste("Results for entity: ", entityName, " with calculated regression model"), color = "Architecture variation", shape ="Load level [req/s]") +
    theme(plot.title = element_text(size = 24),
          axis.title = element_text(size = 20),
          axis.text = element_text(colour = 1, size = 20),
          legend.position = "inside",
          legend.position.inside = legendPosValues,
          legend.spacing.y = unit(0, "mm"), 
          legend.title = element_text(size = 20, face = "bold"),
          legend.text = element_text(size = 20),
          legend.background = element_blank(),
          legend.box.background = element_rect(colour = "black")) +
    geom_abline(slope = coef(linearModel)[[2]], 
            intercept = coef(linearModel)[["(Intercept)"]],
            linetype="dashed")
  
}

reportLinearModel <- function(data, entityName, form) {
  
    linearModel = lm(formula(form), data = data %>% filter(entityName == {{entityName}})) # linear regression
    msummary(list("Model"=linearModel), output = 'kableExtra',
         stars = TRUE,
         title = paste("Linear regresssion model for the entity: ", entityName), gof_omit = 'IC|Log|RMSE')
  
}

```

# Results

## Hypothesis 1

**A higher service replication has a positive impact on time-behavior.**

<details>
  <summary>Deployment topology info</summary>
  
  **noreplication - 20250214_131514**
  
  Pods:

  "teastore-auth-848dd67cc7-8fjjq": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
  "teastore-db-855687f49f-9k9wt": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
  "teastore-image-758c554dc-8mkrm": "i-0ee51be2234fa8253.us-east-2.compute.internal": "us-east-2b"  
  "teastore-persistence-648b7cb468-cq75p": "i-0a291269f6692f301.us-east-2.compute.internal": "us-east-2b"  
  "teastore-recommender-5cff6fcd6c-vh9jn": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
  "teastore-registry-7cd6c95dd4-67x9m": "i-0ccfdc108f890e91b.us-east-2.compute.internal": "us-east-2c"  
  "teastore-webui-565dc9497f-gtdn4": "i-0c32bc7124cc190fa.us-east-2.compute.internal": "us-east-2c"  
  
  
  **noreplication - 20250214_144959**
  
  Pods:

  "teastore-auth-848dd67cc7-pz26g": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
  "teastore-db-855687f49f-jt26p": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
  "teastore-image-758c554dc-2z654": "i-0ee51be2234fa8253.us-east-2.compute.internal": "us-east-2b"  
  "teastore-persistence-648b7cb468-zfdjh": "i-0a699b05582d3e038.us-east-2.compute.internal": "us-east-2b"  
  "teastore-recommender-5cff6fcd6c-fn9wp": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
  "teastore-registry-7cd6c95dd4-jb4hr": "i-0b4483458f7db6913.us-east-2.compute.internal": "us-east-2b"  
  "teastore-webui-565dc9497f-wcdkk": "i-0a291269f6692f301.us-east-2.compute.internal": "us-east-2b"  
  
  **lowreplication - 20250211_120129**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-t76d9": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-5bb98f67f6-vf69s": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-5czs7": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-8ffvw": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-cdmvr": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-98fj8": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-jd7kp": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-mt8bn": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-r5l7n": "i-0800aaede6b61a651.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-6768cc7797-9rpwn": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-ddv5r": "i-093584a5ee8cb2bb8.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-gclds": "i-03dd7245033498046.us-east-2.compute.internal": "us-east-2c"  
  
  **lowreplication - 20250211_135228**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-42fw5": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-m8dwl": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-db-556958c44b-zpszn": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-ct692": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-5bb5dc45c8-vvm4s": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-24htp": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-ql7xl": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-228d4": "i-03dd7245033498046.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-22qlr": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-6768cc7797-tp57k": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-b8xpk": "i-0800aaede6b61a651.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-c4vz4": "i-093584a5ee8cb2bb8.us-east-2.compute.internal": "us-east-2a"  
  
  **mixedreplication - 20250211_153120**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-cqnv9": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-5bb98f67f6-qztvb": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-x9qd6": "i-0800aaede6b61a651.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-5krj7": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-k8z77": "i-093584a5ee8cb2bb8.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-kgh2w": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-5bb5dc45c8-tf2kw": "i-03dd7245033498046.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-9kg9q": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-9xql8": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-867d46c69c-bl7dv": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-g96kx": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-867d46c69c-xrbzc": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-2dfcq": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-6768cc7797-xtlh7": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-gh4x4": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-lvjd2": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-pdfr7": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-tlfnb": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-xpd2z": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
  
  **mixedreplication - 20250211_172157**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-dj975": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-fgxcv": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-5bb98f67f6-s2h5n": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-db-556958c44b-lsq4g": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-r9tmc": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-xffkt": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-z9j52": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-8q2qf": "i-03dd7245033498046.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-ljnwf": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-prhnc": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-scp7d": "i-0800aaede6b61a651.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-t5wq6": "i-093584a5ee8cb2bb8.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-nxsgb": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-6768cc7797-9mdbs": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-88l9s": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-dw9f4": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-gpr7t": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-ncwp5": "i-03dd7245033498046.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-pvg7q": "i-0800aaede6b61a651.us-east-2.compute.internal": "us-east-2b"  

  
  **highreplication - 20250205_221658**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-7ccwf": "i-0661648f871ba0ac3.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-d5bbq": "i-05c1384b2b95fde9a.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-5bb98f67f6-g2xks": "i-0beaa68235f0f37cf.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-5bb98f67f6-mwtvm": "i-050abdc2821c8d300.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-5bb98f67f6-snhfj": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-xx4lw": "i-0661648f871ba0ac3.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-jtv9v": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-5bb5dc45c8-r4wgd": "i-09abde46f7e576e4d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-r6twj": "i-0beaa68235f0f37cf.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-s6jwp": "i-064b789bcaa2704c7.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-x9qjs": "i-05c1384b2b95fde9a.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-22pf7": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-gd8vm": "i-05c1384b2b95fde9a.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-jp2tn": "i-050abdc2821c8d300.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-lv4gb": "i-0beaa68235f0f37cf.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-qhblt": "i-064b789bcaa2704c7.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-d7v96": "i-0644429a20b1e6efb.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-hpg9l": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-58bcb8f966-jhs6g": "i-09abde46f7e576e4d.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-l6mv4": "i-09abde46f7e576e4d.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-lzhxd": "i-0644429a20b1e6efb.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-6768cc7797-mctv2": "i-064b789bcaa2704c7.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-f6z8x": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-gbvfp": "i-0fda770aa52a47c76.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-pplv4": "i-0644429a20b1e6efb.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-qtdj5": "i-0fda770aa52a47c76.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-xttb7": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  

  
  **highreplication - 20250206_000127**
  
  Pods:
  
  "teastore-auth-5bb98f67f6-25w4v": "i-05c1384b2b95fde9a.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-5bb98f67f6-2x6j4": "i-050abdc2821c8d300.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-5bb98f67f6-qzj8t": "i-064b789bcaa2704c7.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-sm4d7": "i-06309724cad339b6b.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-5bb98f67f6-t97k8": "i-0beaa68235f0f37cf.us-east-2.compute.internal": "us-east-2c"  
"teastore-db-556958c44b-d2fwx": "i-0ea99b9b5534ea8d1.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-5bb5dc45c8-4msgg": "i-0644429a20b1e6efb.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-6pk7t": "i-09abde46f7e576e4d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-7sfdq": "i-0fda770aa52a47c76.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-5bb5dc45c8-p8s8d": "i-06309724cad339b6b.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-5bb5dc45c8-r5r5v": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-4fw9m": "i-0fda770aa52a47c76.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-867d46c69c-6kd5x": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-97gnv": "i-0644429a20b1e6efb.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-867d46c69c-pp8sx": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-867d46c69c-x4sch": "i-09abde46f7e576e4d.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-7kwdk": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-58bcb8f966-7vx9h": "i-0661648f871ba0ac3.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-58bcb8f966-cqqkd": "i-0beaa68235f0f37cf.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-58bcb8f966-jlswn": "i-05c1384b2b95fde9a.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-58bcb8f966-wr7w6": "i-064b789bcaa2704c7.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-6768cc7797-95flf": "i-0661648f871ba0ac3.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-68dcx": "i-0be1f418781b62f9d.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-6xh5d": "i-0ecb42505bf89ee14.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-79d7f4fbf4-9pcww": "i-050abdc2821c8d300.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-79d7f4fbf4-q9s7l": "i-0661648f871ba0ac3.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-79d7f4fbf4-ttl7m": "i-06309724cad339b6b.us-east-2.compute.internal": "us-east-2a"  

  
</details>

<details>
  <summary>Results analysis</summary>


```{r "hypothesis1a", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9}

investigateServiceReplicationTimeBehaviour <- function(data) {
  result <- data %>%
    select(-c("success_rate [%]", "median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]", "storageReplicationLevel", "ratioOfCachedDataAggregates","dataReplicationAlongRequestTrace" )) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(serviceReplicationLevel, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis1 <- investigateServiceReplicationTimeBehaviour(rbind(teastorePrivateNlbHighreplication,
                                                                teastorePrivateNlbLowreplication,
                                                                teastorePrivateNlbNoreplication,
                                                                teastorePrivateNlbMixedreplication))

plotResultWithRegression(hypothesis1, "teaStore", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "teaStore", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)

```

```{r "hypothesis1b", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Index Page", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "Index Page", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```
```{r "hypothesis1c", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Show Category", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "Show Category", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```

```{r "hypothesis1d", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "User Login", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "User Login", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```

```{r "hypothesis1e", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Product Page", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "Product Page", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```

```{r "hypothesis1f", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Add Product To Cart", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "Add Product To Cart", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```

```{r "hypothesis1g", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "User Logout", serviceReplicationLevel, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~serviceReplicationLevel, "tr")
reportLinearModel(hypothesis1, "User Logout", `90th_percentile(elapsed) [ms]`~serviceReplicationLevel)
```

```{r "hypothesis1Sa", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9}

plotResultWithRegression(hypothesis1, "teaStore", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "teaStore", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)

```

```{r "hypothesis1Sb", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Index Page", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "Index Page", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

```{r "hypothesis1Sc", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Show Category", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "Show Category", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

```{r "hypothesis1Sd", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "User Login", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "User Login", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

```{r "hypothesis1Se", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Product Page", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "Product Page", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

```{r "hypothesis1Sf", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "Add Product To Cart", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "Add Product To Cart", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

```{r "hypothesis1Sg", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis1, "User Logout", smallestReplicationValue, `90th_percentile(elapsed) [ms]`, `90th_percentile(elapsed) [ms]`~smallestReplicationValue, "tr")
reportLinearModel(hypothesis1, "User Logout", `90th_percentile(elapsed) [ms]`~smallestReplicationValue)
```

</details>

## Hypothesis 2

**A higher service replication has a positive impact on availability**

<details>
  <summary>Deployment topology info</summary>
  
  **withfailures-noreplication - 20250211_211843**
  
  Pods:
  
  "teastore-auth-6bf98c95b6-q7t6l": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-556958c44b-ds9nz": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-6786dc87dd-mjmpl": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-85668f6ff5-lp2rc": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-596679cd76-9tgmr": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-5c94c5ff75-qvq67": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-5fcc94b6d8-h5sv7": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  

  **withfailures-noreplication - 20250211_225327**
  
  Pods:
  
  "teastore-auth-6bf98c95b6-t5hkt": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-8lrfl": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-6786dc87dd-x4dn9": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-85668f6ff5-8wfrf": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-596679cd76-7h5t8": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-5c94c5ff75-mqrzx": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-5fcc94b6d8-66zcb": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
  
  **withfailures-lowreplication - 20250212_083050**
  
  Pods:
  
  "teastore-auth-7ffcc469b-gf4nq": "i-0dbb62adae22c9e13.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-7ffcc469b-rndh7": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-2rg7m": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-79649dbd78-8ncfz": "i-079dc8211f4ef6be8.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-79649dbd78-8qsmm": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5f69985cb9-rrs4g": "i-00c6fbd044d93e1b3.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5f69985cb9-vs4r9": "i-0fff41fcb194f20b1.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5dbbb79d6-nnwxj": "i-063abf83790d97192.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5dbbb79d6-sjbvp": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-6768cc7797-n9zwk": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-57cff659f8-49ncf": "i-0caa4a71bafc850e6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-57cff659f8-9bbg9": "i-03c0d468922fb4d1c.us-east-2.compute.internal": "us-east-2a"  

  
  **withfailures-lowreplication - 20250212_103519**
  
  Pods:
  
  "teastore-auth-7ffcc469b-xpqqb": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-7ffcc469b-zn2gj": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-556958c44b-9pmt8": "i-0fff41fcb194f20b1.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-79649dbd78-8k2lz": "i-0dbb62adae22c9e13.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-79649dbd78-rtldp": "i-063abf83790d97192.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5f69985cb9-dsclv": "i-00c6fbd044d93e1b3.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5f69985cb9-nr7zh": "i-079dc8211f4ef6be8.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5dbbb79d6-6nswd": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5dbbb79d6-kr6zk": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-6768cc7797-hjlcn": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-57cff659f8-vg28p": "i-0caa4a71bafc850e6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-57cff659f8-wqxdw": "i-03c0d468922fb4d1c.us-east-2.compute.internal": "us-east-2a"  

  
  **withfailures-mixedreplication - 20250212_123842**
  
  Pods:
  
  "teastore-auth-7ffcc469b-bdsmg": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-7ffcc469b-j42mz": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-7ffcc469b-ph2h4": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-db-556958c44b-9nqd2": "i-0dbb62adae22c9e13.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-79649dbd78-g5m8l": "i-03c0d468922fb4d1c.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-79649dbd78-k6bks": "i-0fff41fcb194f20b1.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-79649dbd78-rq88z": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5f69985cb9-5h54j": "i-079dc8211f4ef6be8.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5f69985cb9-7wf85": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5f69985cb9-9bx4n": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5f69985cb9-bvq4t": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5f69985cb9-n4fbf": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5dbbb79d6-87mff": "i-063abf83790d97192.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-6768cc7797-hjqhb": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-57cff659f8-c74gf": "i-063abf83790d97192.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-57cff659f8-nkk4k": "i-00c6fbd044d93e1b3.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-57cff659f8-nmjwr": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-57cff659f8-rrzzf": "i-0caa4a71bafc850e6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-57cff659f8-tql8d": "i-079dc8211f4ef6be8.us-east-2.compute.internal": "us-east-2b"  

  
  **withfailures-mixedreplication - 20250212_141420**
  
  Pods:
  
  "teastore-auth-87dfcb769-nrlzq": "i-00c6fbd044d93e1b3.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-87dfcb769-r984l": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-87dfcb769-w9zds": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-855687f49f-zh7gc": "i-079dc8211f4ef6be8.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-865689b5f9-4r6hb": "i-0fff41fcb194f20b1.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-865689b5f9-j8j2f": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-865689b5f9-l4b2x": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-6db778bc9b-5c7j6": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-7rjvf": "i-0dbb62adae22c9e13.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-6db778bc9b-czp6h": "i-055e82373e583b7c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-6db778bc9b-gkmz5": "i-0fff41fcb194f20b1.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-6db778bc9b-mnhwc": "i-0caa4a71bafc850e6.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-866ccfb8b7-s2t5f": "i-0dbb62adae22c9e13.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-9sz2p": "i-063abf83790d97192.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-667586f4bc-5dd2p": "i-00470f34d75ef1893.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-667586f4bc-8zgf8": "i-037ef3f68815edd9e.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-667586f4bc-kj6jb": "i-03c0d468922fb4d1c.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-667586f4bc-q7wbb": "i-04dacda900ee5a9a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-667586f4bc-vdtcf": "i-00a4b38a0b75e4d7d.us-east-2.compute.internal": "us-east-2b"  

  
  **withfailures-highreplication - 20250216_140815**
  
  Pods:
  
  "teastore-auth-87dfcb769-94sfx": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-87dfcb769-fpvvf": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-87dfcb769-jk82s": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-87dfcb769-l4mrd": "i-0f78013de48027657.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-87dfcb769-qbc98": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-855687f49f-qhfrr": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-865689b5f9-5ghc8": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-865689b5f9-bgp9w": "i-04212efe18d867c73.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-865689b5f9-bmxnj": "i-091cb8a89d94113d9.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-865689b5f9-hwpjg": "i-0bcc77b4fd32e103c.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-865689b5f9-tw7qt": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-6db778bc9b-2j8ql": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-6db778bc9b-bw6v9": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-bxk79": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-6db778bc9b-kptkv": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-qz5nx": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-866ccfb8b7-248fk": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-866ccfb8b7-2kjwv": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-866ccfb8b7-fzldw": "i-0f78013de48027657.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-866ccfb8b7-kllks": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-866ccfb8b7-sqw4r": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-7cd6c95dd4-cj8lq": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-667586f4bc-9jdjw": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-667586f4bc-dwbdt": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-667586f4bc-pmknk": "i-091cb8a89d94113d9.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-667586f4bc-qkbtt": "i-0bcc77b4fd32e103c.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-667586f4bc-zwrtb": "i-04212efe18d867c73.us-east-2.compute.internal": "us-east-2a"  

  
  **withfailures-highreplication - 20250216_154310**
  
  Pods:
  
  "teastore-auth-87dfcb769-4qbll": "i-0f78013de48027657.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-87dfcb769-7btc8": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-87dfcb769-kf7kt": "i-0bcc77b4fd32e103c.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-87dfcb769-ltsl6": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-87dfcb769-pp9dm": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-855687f49f-hgc6p": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-865689b5f9-6tjk7": "i-091cb8a89d94113d9.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-865689b5f9-cmrsl": "i-04212efe18d867c73.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-865689b5f9-hq2xl": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-865689b5f9-kxkc5": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-865689b5f9-z2r6r": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-8knsc": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-6db778bc9b-b7tv2": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-c5kwf": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-6db778bc9b-ggx46": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-6db778bc9b-tqpt5": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-866ccfb8b7-5qq6n": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-866ccfb8b7-7b8wh": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-866ccfb8b7-cgcrg": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-866ccfb8b7-qlthd": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-866ccfb8b7-rph62": "i-0f78013de48027657.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-wnj2c": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-667586f4bc-cs46z": "i-0bcc77b4fd32e103c.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-667586f4bc-pk8t2": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-667586f4bc-v4jww": "i-04212efe18d867c73.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-667586f4bc-vj7gg": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-667586f4bc-wb8km": "i-091cb8a89d94113d9.us-east-2.compute.internal": "us-east-2c"  
  
</details>


<details>
  <summary>Results analysis</summary>

```{r "hypothesis2a", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}

investigateServiceReplicationAvailability <- function(data) {
  result <- data %>%
    select(-c("mean(elapsed) [ms]","median(elapsed) [ms]","90th_percentile(elapsed) [ms]","median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]","throughput [requests / s]", "storageReplicationLevel", "ratioOfCachedDataAggregates","dataReplicationAlongRequestTrace" )) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(serviceReplicationLevel, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis2 <- investigateServiceReplicationAvailability(rbind(teastorePrivateNlbWithfailuresHighreplication,
                                                               teastorePrivateNlbWithfailuresLowreplication,
                                                               teastorePrivateNlbWithfailuresNoreplication,
                                                               teastorePrivateNlbWithfailuresMixedreplication))

plotResultWithRegression(hypothesis2, "teaStore", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "teaStore", `success_rate [%]`~serviceReplicationLevel)
```

```{r "hypothesis2b", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}

plotResultWithRegression(hypothesis2, "Index Page", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "Index Page", `success_rate [%]`~serviceReplicationLevel)

```

```{r "hypothesis2c", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis2, "Show Category", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "Show Category", `success_rate [%]`~serviceReplicationLevel)
```

```{r "hypothesis2d", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis2, "User Login", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "User Login", `success_rate [%]`~serviceReplicationLevel)
```

```{r "hypothesis2e", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis2, "Product Page", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "Product Page", `success_rate [%]`~serviceReplicationLevel)
```

```{r "hypothesis2f", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis2, "Add Product To Cart", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "Add Product To Cart", `success_rate [%]`~serviceReplicationLevel)
```

```{r "hypothesis2g", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis2, "User Logout", serviceReplicationLevel, `success_rate [%]`, `success_rate [%]`~serviceReplicationLevel, "br")
reportLinearModel(hypothesis2, "User Logout", `success_rate [%]`~serviceReplicationLevel)
```

</details>

## Hypothesis 3

**A higher horizontal data replication has a positive impact on time-behavior**

<details>
  <summary>Deployment topology info</summary>
  
  **rds-single-noreplication - 20250222_215712**
  
  Pods:

"teastore-auth-848dd67cc7-lxhn7": "i-09abd13e476f914ef.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-dk769": "i-06a382464f979a9f8.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-82cbw": "i-03a615ae0375955a4.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-nj8ss": "i-0d274c4bfe09259f9.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-fb9sv": "i-038b3f842b19ad8fa.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-p5nqw": "i-00fcd7aba957c6c1b.us-east-2.compute.internal": "us-east-2b"  

  RDS instances:

"maria-db": "us-east-2a"
  
  **rds-single-noreplication - 20250222_233449**
  
  Pods:
  
  "teastore-auth-848dd67cc7-r2wqw": "i-06a382464f979a9f8.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-8bm84": "i-00fcd7aba957c6c1b.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-h8ghd": "i-0d274c4bfe09259f9.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-ngc9b": "i-09abd13e476f914ef.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-crx55": "i-038b3f842b19ad8fa.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-4sqmv": "i-06f896998f8ee9876.us-east-2.compute.internal": "us-east-2b"  

  RDS instances:

"maria-db": "us-east-2a"
  
  **rds-two-noreplication - 20250223_151849**
  
  Pods:
  
  "teastore-auth-848dd67cc7-nxwp9": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-qgxfb": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-5fjxq": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-sz8rj": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-kdmwb": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-wvtzk": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
  
  **rds-two-noreplication - 20250223_165204**
  
  Pods:
  
  "teastore-auth-848dd67cc7-k6vn2": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-ww7dw": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-c94r7": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-cz6cl": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-jdr2b": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-9k9rk": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  

  RDS instance:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
  
  **rds-three-noreplication - 20250223_220301**
  
  Pods:
  
  "teastore-auth-848dd67cc7-6prnr": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-9g6c9": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-bpbv6": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-2wvfw": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-vmj4k": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-j9dd9": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
"second-read-replica": "us-east-2b"  
  
  **rds-three-noreplication - 20250223_233533**
  
  Pods:
  
  "teastore-auth-848dd67cc7-q5zzb": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-27f4n": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-nv9ft": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-5v4zb": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-226wh": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-f6dqk": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
"second-read-replica": "us-east-2b"  
  
  **rds-single-highreplication - 20250223_115228**
  
  Pods:
  
  "teastore-auth-848dd67cc7-2h8mq": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-49cx2": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-8njpk": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-d42rk": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-j682w": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-khvn7": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-mwflr": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-r5nbn": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-r7pqg": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-w6h96": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-4497t": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-9qmvl": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-nvvjj": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-pr7zc": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-v95j8": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-27cm8": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-5s9gr": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-86dxs": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-dfghv": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-fdslb": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-w4l7n": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-8rgwn": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-c5nxx": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-mb7cw": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-pkqzf": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-qg9fn": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  

RDS instances:

"maria-db": "us-east-2a"  
  
  **rds-single-highreplication - 20250223_133601**
  
  Pods:
  
  "teastore-auth-848dd67cc7-2qdnf": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-jtvtt": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-m44tk": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-mcgtl": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-zskqs": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-4qmdv": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-59fr7": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-96wph": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-ps4nq": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-wdc44": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-cj7gg": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-ltrqz": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-nzcgm": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-r52wc": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-snsd6": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-2h85h": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-jg4bl": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-m982d": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-rgwwh": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-x4zmd": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-6ztsw": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-9clwd": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-jttx9": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-pvgz9": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-rcgq4": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-txp29": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  

RDS instances:

"maria-db": "us-east-2a"  
  
  **rds-two-highreplication - 20250223_184333**
  
  Pods:

"teastore-auth-848dd67cc7-5spxc": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-bnw9n": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-gcpfs": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-qxz26": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-s9zx6": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-8zl5m": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-9n5mr": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-hnbdj": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-lz4p5": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-x6knh": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-52bgd": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-9xzk7": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-mthtm": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-n6gr9": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-zgmt5": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-6md2n": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-hp82l": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-lprpp": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-lww4l": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-t2kfn": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-9g8kt": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-klk77": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-kr9t8": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-mjndm": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-prxws": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-z9sqn": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  

RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
  
  **rds-two-highreplication - 20250223_201822**
  
  Pods:
  
  "teastore-auth-848dd67cc7-4296m": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-67bvf": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-f9gs7": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-fx45x": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-l6x8n": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-kfjc8": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-kvnzp": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-n6zdd": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-rp5t4": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-t48ns": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-4tbk4": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-7fll2": "i-0246d3c1c4d3f8b1b.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-cw6cz": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-g6pnb": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-jp9tn": "i-05e9858c9b746747f.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-5qz2b": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-j2sxj": "i-05595423e7c999a38.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-lqcp8": "i-050930becc565b4f2.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-qntzs": "i-072261d708765039a.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-rs5p4": "i-0f075de11fd6646d6.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-7cd6c95dd4-5jb68": "i-0bc6cae9e6dd93dc5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-8vs79": "i-058c42ee0b437c176.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-9528b": "i-0d5b7bdb5abf83489.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-gdqpj": "i-026d8db45140a2320.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-jcg6j": "i-058927ad95dd1d084.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-pwqhx": "i-0f763fc1bbf428b57.us-east-2.compute.internal": "us-east-2c"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
  
  **rds-three-highreplication - 20250224_120738**
  
  Pods:
  
  "teastore-auth-848dd67cc7-2nqd9": "i-008c6485516911de4.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-5vzk4": "i-0a94b1678624a7db5.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-br2pv": "i-0132a1e73c173edd4.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-m9v9z": "i-09567f5e50770a3af.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-pq7mk": "i-070cefe4ae5854354.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-8r28g": "i-0ff0aac53ae49f664.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-g2cvg": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-hrfxx": "i-0dd42f05db5bcb273.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-lhbwk": "i-0beac53d5158a61df.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-pjhsn": "i-014e6fa661c5d7744.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-5pw7h": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-8hj8j": "i-014e6fa661c5d7744.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-tqv8k": "i-0de1892bc1a7136dc.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-ww8v7": "i-0a94b1678624a7db5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-xms6d": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-59nlq": "i-0de1892bc1a7136dc.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-5q5kf": "i-0a94b1678624a7db5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-g4kqv": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-sv268": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-v88nw": "i-0132a1e73c173edd4.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-jcd2j": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-2l9wf": "i-070cefe4ae5854354.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-c4txg": "i-0beac53d5158a61df.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-hcdvj": "i-0dd42f05db5bcb273.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-kcbc8": "i-09567f5e50770a3af.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-kqlmw": "i-008c6485516911de4.us-east-2.compute.internal": "us-east-2b"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
"second-read-replica": "us-east-2b"  

  **rds-three-highreplication - 20250224_133907**
  
  Pods:
  
  "teastore-auth-848dd67cc7-52hpj": "i-0dd42f05db5bcb273.us-east-2.compute.internal": "us-east-2a"  
"teastore-auth-848dd67cc7-5lvzx": "i-09567f5e50770a3af.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-6h7l5": "i-0beac53d5158a61df.us-east-2.compute.internal": "us-east-2b"  
"teastore-auth-848dd67cc7-p69bx": "i-014e6fa661c5d7744.us-east-2.compute.internal": "us-east-2c"  
"teastore-auth-848dd67cc7-rn7g6": "i-008c6485516911de4.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-2ggq9": "i-0de1892bc1a7136dc.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-47dnl": "i-008c6485516911de4.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-7vf8c": "i-0ff0aac53ae49f664.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-h55t2": "i-0a94b1678624a7db5.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-jfmf8": "i-070cefe4ae5854354.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-7zr7z": "i-070cefe4ae5854354.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-5cb4574b98-dfhj5": "i-0de1892bc1a7136dc.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-5cb4574b98-mvznq": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-s547w": "i-0a94b1678624a7db5.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-5cb4574b98-spkfg": "i-0132a1e73c173edd4.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-69grf": "i-0132a1e73c173edd4.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-bfwkj": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-sjfk5": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-w9jbn": "i-0beac53d5158a61df.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-xpmm9": "i-09567f5e50770a3af.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-7cd6c95dd4-n9wq7": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-6trbf": "i-0ff0aac53ae49f664.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-9qcsf": "i-014e6fa661c5d7744.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-chw49": "i-0dd42f05db5bcb273.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-565dc9497f-cvtf8": "i-03bb2e488f46e37e5.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-gv5j7": "i-07f303a2dbcc8912e.us-east-2.compute.internal": "us-east-2a"  

  RDS instances:

"maria-db": "us-east-2c"  
"first-read-replica": "us-east-2a"  
"second-read-replica": "us-east-2b"  
 
</details>

<details>
  <summary>Results analysis</summary>

```{r "hypothesis3La", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}

investigateHorizontalReplicationTimeBehaviour <- function(data) {
  result <- data %>%
    select(-c("success_rate [%]", "median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "ratioOfCachedDataAggregates","dataReplicationAlongRequestTrace" )) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(storageReplicationLevel, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis3a <- investigateHorizontalReplicationTimeBehaviour(rbind(teastorePrivateNlbRdsSingleNoreplication,
                                                                    teastorePrivateNlbRdsTwoNoreplication,
                                                                    teastorePrivateNlbRdsThreeNoreplication))

plotResultWithRegression(hypothesis3a, "teaStore", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "teaStore", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Lb", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3a, "Index Page", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "Index Page", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Lc", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3a, "Show Category", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "Show Category", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Ld", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3a, "User Login", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "User Login", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Le", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3a, "Product Page", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "Product Page", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Lf", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3a, "Add Product To Cart", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3a, "Add Product To Cart", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

For the entity *User Logout*, the measure *storageReplicationLevel* is undefined, because the request trace does not call a database.


```{r "hypothesis3Ha", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}

investigateHorizontalReplicationTimeBehaviour <- function(data) {
  result <- data %>%
    select(-c("success_rate [%]", "median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "ratioOfCachedDataAggregates","dataReplicationAlongRequestTrace" )) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(storageReplicationLevel, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis3b <- investigateHorizontalReplicationTimeBehaviour(rbind(teastorePrivateNlbRdsSingleHighreplication,
                                                                     teastorePrivateNlbRdsTwoHighreplication,
                                                                     teastorePrivateNlbRdsThreeHighreplication))

plotResultWithRegression(hypothesis3b, "teaStore", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "teaStore", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)

```

```{r "hypothesis3Hb", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3b, "Index Page", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "Index Page", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Hc", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3b, "Show Category", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "Show Category", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Hd", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3b, "User Login", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "User Login", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3He", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3b, "Product Page", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "Product Page", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

```{r "hypothesis3Hf", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis3b, "Add Product To Cart", storageReplicationLevel, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~storageReplicationLevel, "tr")
reportLinearModel(hypothesis3b, "Add Product To Cart", `90th_percentile(elapsed) [ms]`~storageReplicationLevel)
```

For the entity *User Logout*, the measure *storageReplicationLevel* is undefined, because the request trace does not call a database.

</details>

## Hypothesis 4

**A higher vertical data replication has a positive impact on time-behavior**

<details>
  <summary>Deployment topology info</summary>
  
  **noreplication-nocaching - 20250213_144548**
  
  Pods:
  
  "teastore-auth-848dd67cc7-nn9vb": "i-0c1102daeb141599b.us-east-2.compute.internal": "us-east-2c"  
"teastore-db-855687f49f-575cv": "i-0531150bc7899e2a7.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-zzm25": "i-0209b13fb444c1d5e.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-86c596fdb5-nnhjg": "i-0486cd8db243ec727.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-kx5ld": "i-0280562c24c16ada7.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-9p8xv": "i-0719bcaa5f410ea61.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-565dc9497f-d2mbh": "i-068e606dda4f85eb5.us-east-2.compute.internal": "us-east-2a"  
  
  **noreplication-nocaching - 20250213_163214**
  
  Pods:
  
  "teastore-auth-848dd67cc7-qkjnf": "i-0486cd8db243ec727.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-855687f49f-24wds": "i-0280562c24c16ada7.us-east-2.compute.internal": "us-east-2a"  
"teastore-image-758c554dc-jsvpw": "i-0719bcaa5f410ea61.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-86c596fdb5-ww5rz": "i-0209b13fb444c1d5e.us-east-2.compute.internal": "us-east-2c"  
"teastore-recommender-5cff6fcd6c-p5frt": "i-068e606dda4f85eb5.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-7cd6c95dd4-9lzhp": "i-0c1102daeb141599b.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-565dc9497f-pkxkd": "i-0531150bc7899e2a7.us-east-2.compute.internal": "us-east-2c"  
  
   **noreplication - 20250214_131514**
  
  Pods:

  "teastore-auth-848dd67cc7-8fjjq": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
  "teastore-db-855687f49f-9k9wt": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
  "teastore-image-758c554dc-8mkrm": "i-0ee51be2234fa8253.us-east-2.compute.internal": "us-east-2b"  
  "teastore-persistence-648b7cb468-cq75p": "i-0a291269f6692f301.us-east-2.compute.internal": "us-east-2b"  
  "teastore-recommender-5cff6fcd6c-vh9jn": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
  "teastore-registry-7cd6c95dd4-67x9m": "i-0ccfdc108f890e91b.us-east-2.compute.internal": "us-east-2c"  
  "teastore-webui-565dc9497f-gtdn4": "i-0c32bc7124cc190fa.us-east-2.compute.internal": "us-east-2c"  
  
  **noreplication - 20250214_144959**
  
  Pods:

  "teastore-auth-848dd67cc7-pz26g": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
  "teastore-db-855687f49f-jt26p": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
  "teastore-image-758c554dc-2z654": "i-0ee51be2234fa8253.us-east-2.compute.internal": "us-east-2b"  
  "teastore-persistence-648b7cb468-zfdjh": "i-0a699b05582d3e038.us-east-2.compute.internal": "us-east-2b"  
  "teastore-recommender-5cff6fcd6c-fn9wp": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
  "teastore-registry-7cd6c95dd4-jb4hr": "i-0b4483458f7db6913.us-east-2.compute.internal": "us-east-2b"  
  "teastore-webui-565dc9497f-wcdkk": "i-0a291269f6692f301.us-east-2.compute.internal": "us-east-2b" 
  
  **noreplication-withcaching - 20250214_214037**
  
  Pods:
  
  "teastore-auth-848dd67cc7-7btrc": "i-0b4483458f7db6913.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-855687f49f-7x4vq": "i-0eacd28b21f62c162.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-45q9l": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-86c596fdb5-t2vt7": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-g2knx": "i-0ccfdc108f890e91b.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-7cd6c95dd4-5tdzc": "i-0a699b05582d3e038.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-559bf8c4c9-gjk8v": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
  
  **noreplication-withcaching - 20250214_231501**
  
  Pods:
  
"teastore-auth-848dd67cc7-qvcnw": "i-032693167aaef27a6.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-855687f49f-h7g47": "i-0b4483458f7db6913.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-758c554dc-2kz9s": "i-07f8e5b25efa587a4.us-east-2.compute.internal": "us-east-2a"  
"teastore-persistence-86c596fdb5-c8t7n": "i-0ed3df51bfcdd4308.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-m5cbk": "i-0c32bc7124cc190fa.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-7cd6c95dd4-8sg8k": "i-0ee51be2234fa8253.us-east-2.compute.internal": "us-east-2b"  
"teastore-webui-559bf8c4c9-jm99d": "i-0eacd28b21f62c162.us-east-2.compute.internal": "us-east-2b"  
  
  **noreplication-withmorecaching - 20250216_172156**
  
  Pods:
  
  "teastore-auth-848dd67cc7-xcms8": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-855687f49f-fn59m": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-rpnp4": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"  
"teastore-persistence-86c596fdb5-j97rw": "i-0f78013de48027657.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-5cff6fcd6c-scq22": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-rrf2l": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-559bf8c4c9-gl7fg": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
  
  **noreplication-withmorecaching - 20250216_185257**

  Pods:
  
  "teastore-auth-848dd67cc7-gltdk": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-855687f49f-5lhcs": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-758c554dc-2kzsj": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-86c596fdb5-rn25w": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"  
"teastore-recommender-5cff6fcd6c-zbh9r": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"  
"teastore-registry-7cd6c95dd4-frhp5": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-559bf8c4c9-mcs4v": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"  
  
</details>

<details>
  <summary>Results analysis</summary>

```{r "hypothesis4a", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
investigateVerticalReplicationTimeBehaviour <- function(data) {
  result <- data %>%
    select(-c("success_rate [%]", "median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel")) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(ratioOfCachedDataAggregates,dataReplicationAlongRequestTrace,, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis4 <- investigateVerticalReplicationTimeBehaviour(rbind(teastorePrivateNlbNoreplicationWithcaching,
                                                                 teastorePrivateNlbNoreplicationNocaching,
                                                                 teastorePrivateNlbNoreplicationWithmorecaching,
                                                                 teastorePrivateNlbNoreplication))

plotResultWithRegression(hypothesis4, "teaStore", ratioOfCachedDataAggregates, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~ratioOfCachedDataAggregates, "tr")
reportLinearModel(hypothesis4, "teaStore", `90th_percentile(elapsed) [ms]`~ratioOfCachedDataAggregates)
```


```{r "hypothesis4b", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "Index Page", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "Index Page", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis4c", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "Show Category", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "Show Category", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```


```{r "hypothesis4d", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "User Login", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "User Login", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis4e", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "Product Page", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "Product Page", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis4f", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "Add Product To Cart", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "Add Product To Cart", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis4g", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis4, "User Logout", dataReplicationAlongRequestTrace, `90th_percentile(elapsed) [ms]`,`90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace, "tr")
reportLinearModel(hypothesis4, "User Logout", `90th_percentile(elapsed) [ms]`~dataReplicationAlongRequestTrace)
```

</details>

## Hypothesis 5

**A higher vertical data replication has a positive impact on availability**

<details>
  <summary>Deployment topology info</summary>
  
  **withfailures-nocaching - 20250216_202723**
  
  Pods:
  
  "teastore-auth-87dfcb769-69jnn": "i-0f84400790f50a53a.us-east-2.compute.internal": "us-east-2c"
"teastore-db-855687f49f-46stv": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"
"teastore-image-865689b5f9-jxwtq": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"
"teastore-persistence-6b7b44f867-wlt47": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"
"teastore-recommender-866ccfb8b7-vzc4x": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"
"teastore-registry-7cd6c95dd4-kswpg": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"
"teastore-webui-667586f4bc-sbmwh": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"
  
  **withfailures-nocaching - 20250216_220729**
  
  Pods:
  
  "teastore-auth-87dfcb769-kwpcd": "i-0eea8168ecf59a0f5.us-east-2.compute.internal": "us-east-2b"
"teastore-db-855687f49f-st4dm": "i-058d54abeb60378b8.us-east-2.compute.internal": "us-east-2b"
"teastore-image-865689b5f9-x4cn8": "i-08bec42205851b191.us-east-2.compute.internal": "us-east-2a"
"teastore-persistence-6b7b44f867-lvqv9": "i-09bb2bb3b5ad10cde.us-east-2.compute.internal": "us-east-2b"
"teastore-recommender-866ccfb8b7-449k2": "i-0768fff0eee1ba0f6.us-east-2.compute.internal": "us-east-2c"
"teastore-registry-7cd6c95dd4-zplkh": "i-0ea5be9d4edeec5c0.us-east-2.compute.internal": "us-east-2a"
"teastore-webui-667586f4bc-cn25f": "i-0908d5f5c78691949.us-east-2.compute.internal": "us-east-2c"
  
  **withfailures-noreplication - 20250211_211843**
  
  Pods:
  
  "teastore-auth-6bf98c95b6-q7t6l": "i-0623f7a395494d30b.us-east-2.compute.internal": "us-east-2a"  
"teastore-db-556958c44b-ds9nz": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-image-6786dc87dd-mjmpl": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-85668f6ff5-lp2rc": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-596679cd76-9tgmr": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
"teastore-registry-5c94c5ff75-qvq67": "i-020e6aa1ee89a5353.us-east-2.compute.internal": "us-east-2a"  
"teastore-webui-5fcc94b6d8-h5sv7": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  

  **withfailures-noreplication - 20250211_225327**
  
  Pods:
  
  "teastore-auth-6bf98c95b6-t5hkt": "i-06d65a5f60c8f002a.us-east-2.compute.internal": "us-east-2b"  
"teastore-db-556958c44b-8lrfl": "i-036731fbc0207c44d.us-east-2.compute.internal": "us-east-2c"  
"teastore-image-6786dc87dd-x4dn9": "i-09cd6681256292b99.us-east-2.compute.internal": "us-east-2b"  
"teastore-persistence-85668f6ff5-8wfrf": "i-0129785a4d7128700.us-east-2.compute.internal": "us-east-2b"  
"teastore-recommender-596679cd76-7h5t8": "i-0be7001d7817d65df.us-east-2.compute.internal": "us-east-2c"  
"teastore-registry-5c94c5ff75-mqrzx": "i-0a0a3b9142a732fe8.us-east-2.compute.internal": "us-east-2c"  
"teastore-webui-5fcc94b6d8-66zcb": "i-02f692eef2366b5df.us-east-2.compute.internal": "us-east-2a"  
  
  **withfailures-withcaching - 20250217_091525**
  
  Pods:
  
  "teastore-auth-87dfcb769-7zfcx": "i-0c5b3c188b28a91d2.us-east-2.compute.internal": "us-east-2c"
"teastore-db-855687f49f-pbfnr": "i-08e0048418f8a377d.us-east-2.compute.internal": "us-east-2b"
"teastore-image-865689b5f9-9f947": "i-035541a7496650e30.us-east-2.compute.internal": "us-east-2a"
"teastore-persistence-6b7b44f867-5kr4m": "i-04c1e187a171c4969.us-east-2.compute.internal": "us-east-2b"
"teastore-recommender-866ccfb8b7-zlllc": "i-0166a1c0a10387453.us-east-2.compute.internal": "us-east-2a"
"teastore-registry-7cd6c95dd4-r57gb": "i-073993bd0d8f5ee41.us-east-2.compute.internal": "us-east-2a"
"teastore-webui-cb5d755bc-cw5bc": "i-00a3b9e21c4024a85.us-east-2.compute.internal": "us-east-2c"
  
  **withfailures-withcaching - 20250217_112514**
  
  Pods:
  
  "teastore-auth-87dfcb769-n4cqw": "i-08e0048418f8a377d.us-east-2.compute.internal": "us-east-2b"
"teastore-db-855687f49f-ttt7m": "i-0166a1c0a10387453.us-east-2.compute.internal": "us-east-2a"
"teastore-image-865689b5f9-7fkjk": "i-073993bd0d8f5ee41.us-east-2.compute.internal": "us-east-2a"
"teastore-persistence-6b7b44f867-l9plb": "i-00a3b9e21c4024a85.us-east-2.compute.internal": "us-east-2c"
"teastore-recommender-866ccfb8b7-wcnfj": "i-0c5cac054c83da12e.us-east-2.compute.internal": "us-east-2b"
"teastore-registry-7cd6c95dd4-bkw5r": "i-035541a7496650e30.us-east-2.compute.internal": "us-east-2a"
"teastore-webui-cb5d755bc-zb929": "i-0c5b3c188b28a91d2.us-east-2.compute.internal": "us-east-2c"
  
  **withfailures-withmorecaching - 20250217_130126**
  
  Pods:
  
  "teastore-auth-5c5469cc77-jdrl2": "i-06d5fde1806e27322.us-east-2.compute.internal": "us-east-2b"
"teastore-db-855687f49f-4pcnk": "i-04c1e187a171c4969.us-east-2.compute.internal": "us-east-2b"
"teastore-image-865689b5f9-wvj8s": "i-07c7922247e0b3abf.us-east-2.compute.internal": "us-east-2c"
"teastore-persistence-6b7b44f867-kjl94": "i-0166a1c0a10387453.us-east-2.compute.internal": "us-east-2a"
"teastore-recommender-866ccfb8b7-z8p4n": "i-03cb0f63b09008cd7.us-east-2.compute.internal": "us-east-2c"
"teastore-registry-7cd6c95dd4-44t92": "i-0f51de9306b532fea.us-east-2.compute.internal": "us-east-2a"
"teastore-webui-cb5d755bc-rv5t6": "i-073993bd0d8f5ee41.us-east-2.compute.internal": "us-east-2a"
  
  **withfailures-withmorecaching - 20250217_152335**
  
  Pods:
  
  "teastore-auth-5c5469cc77-gt22c": "i-035541a7496650e30.us-east-2.compute.internal": "us-east-2a"
"teastore-db-855687f49f-shxt7": "i-0166a1c0a10387453.us-east-2.compute.internal": "us-east-2a"
"teastore-image-865689b5f9-94xdc": "i-08e0048418f8a377d.us-east-2.compute.internal": "us-east-2b"
"teastore-persistence-6b7b44f867-ztgb6": "i-00a3b9e21c4024a85.us-east-2.compute.internal": "us-east-2c"
"teastore-recommender-866ccfb8b7-x7ldd": "i-0f51de9306b532fea.us-east-2.compute.internal": "us-east-2a"
"teastore-registry-7cd6c95dd4-ndx48": "i-0c5b3c188b28a91d2.us-east-2.compute.internal": "us-east-2c"
"teastore-webui-cb5d755bc-vz4cd": "i-073993bd0d8f5ee41.us-east-2.compute.internal": "us-east-2a"
  
</details>

<details>
  <summary>Results analysis</summary>

```{r "hypothesis5a", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
investigateVerticalReplicationAvailability <- function(data) {
  result <- data %>%
    select(-c("mean(elapsed) [ms]","median(elapsed) [ms]","90th_percentile(elapsed) [ms]","median(sentBytes) [byte]", "90th_percentile(sentBytes) [byte]","throughput [requests / s]", "serviceReplicationLevel", "medianServiceReplication", "smallestReplicationValue", "storageReplicationLevel" )) %>%
    relocate("entityType", "entityName", "label", .before="architectureVariation") %>%
    group_by(entityType, entityName) %>% 
    arrange(ratioOfCachedDataAggregates,dataReplicationAlongRequestTrace,, .by_group=TRUE, .locale = "en")
  return(result)
}

hypothesis5 <- investigateVerticalReplicationAvailability(rbind(teastorePrivateNlbWithfailuresWithcaching,
                                                                teastorePrivateNlbWithfailuresNocaching,
                                                                teastorePrivateNlbWithfailuresWithmorecaching,
                                                                teastorePrivateNlbWithfailuresNoreplication))

plotResultWithRegression(hypothesis5, "teaStore", ratioOfCachedDataAggregates, `success_rate [%]`,`success_rate [%]`~ratioOfCachedDataAggregates, "br")
reportLinearModel(hypothesis5, "teaStore", `success_rate [%]`~ratioOfCachedDataAggregates)

```


```{r "hypothesis5b", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "Index Page", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "Index Page", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis5c", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "Show Category", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "Show Category", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis5d", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "User Login", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "User Login", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis5e", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "Product Page", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "Product Page", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis5f", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "Add Product To Cart", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "Add Product To Cart", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

```{r "hypothesis5g", echo = FALSE, message=FALSE, fig.asp = 0.8, fig.width = 9, rows.print = 12}
plotResultWithRegression(hypothesis5, "User Logout", dataReplicationAlongRequestTrace, `success_rate [%]`,`success_rate [%]`~dataReplicationAlongRequestTrace, "br")
reportLinearModel(hypothesis5, "User Logout", `success_rate [%]`~dataReplicationAlongRequestTrace)
```

</details>


